\documentclass{jcgcv}

\begin{document}

\fontsize{8pt}{1.15em}
\fontfamily{phv}
\selectfont
\pagenumbering{gobble}
\setlist[itemize]{leftmargin=0.32cm, label={-}}

\begin{column}

  \name{James Grant}

\end{column}\begin{column}

  \fixTop
  \begin{flushright}
    \myhref{mailto:james@jcgrant.com}{james@jcgrant.com}\\
    \myhref{https://www.jcgrant.com}{www.jcgrant.com}\\
    (+44) 07716764153\\
    London + Remote\\
  \end{flushright}

\end{column}\begin{column}

\section{Work}
  \datedsubsection{Senior Software Engineer - Freelance}{2024 - present}
  \begin{itemize}
    \item Wrote a virtual avatar app, using the user's camera, microphone level,
          and machine learning to puppeteer the character in real-time.
    \item Wrote and deployed a task management system on K8S, enabling
          users to view analytics of their workflows, and optimise their time.
  \end{itemize}

  \datedsubsection{Senior Software Engineer - Odin Vision}{2023 - 2024}
  \begin{itemize}
    \item Rearchitected Machine Learning pipelines by breaking up monolithic
          services into smaller microservices; increasing FPS performance on
          the client, and overall data throughput.
    \item Rearchitected the ML team's code into a central repo, enabling greater
          collaboration between the Dev and ML teams, and leading to far less
          mistakes being made while deploying new models to production.
    \item Restructured git repos and Dockerfiles, enabling a greater developer
          experience, and simpler deployments to Kubernetes.
    \item Learnt how to manage K8S on GCP, and the related tools like Helm.
  \end{itemize}

  \datedsubsection{Computer Science Educator - Freelance}{2022 - 2023}
  \begin{itemize}
    \item Wrote, marketed, and sold bespoke one-on-one courses on Computer
          Science, and best modern Software Engineering practices.
  \end{itemize}

  \datedsubsection{Senior Software Engineer - Kidsloop}{2021 - 2022}
  \begin{itemize}
    \item Refactored the entire networking stack of a full stack React app, fixing
          dozens of bugs which had been breaking production for months.
    \item Refactored the WebRTC service by removing it's state, using the new
          networking stack, increasing possible video-chat sizes by 10x.
    \item Built a high throughput distributed data processing pipeline, in Rust.
    \item Built Rust libraries which compiled to both Python and Typescript.
  \end{itemize}

  \datedsubsection{Content Creator - Self Employed}{2020 - present}
  \begin{itemize}
    \item Learnt new creative skills like creative coding, digital art, live streaming.
    \item Grew a successful Social Media presence of over 200,000 followers.
  \end{itemize}

  \datedsubsection{Senior ML Software Engineer - Babylon Health}{2019 - 2020}
  \begin{itemize}
    \item Rewrote the Medical Large Language Model software pipeline.
    \item Built a deployment service, which enabled quick editing and testing of
          different software pipelines via a simple YAML specification.
    \item Wrote a Visual Programming Language to allow designers to create
          complex Amazon Alexa Skills, without code, shortening R\&D cycles.
    \item Rewrote an internal HTTP library, fixing many concurrency bugs.
    \item Introduced type safe Python, which reduced many edge-case bugs.
  \end{itemize}

  \datedsubsection{Research Engineer - Emotech}{2017 - 2018}
  \begin{itemize}
    \item Built a Visual Programming Language to allow designers to create
          complex behaviour, without code, for a smart-home robot assistant,
          shortening R\&D cycles from days/weeks to hours/minutes.
    \item Built a Natural Language Generation Engine, which augments the
          robot's speech with contextual information, and a hint of personality.
    \item Introduced Trello to my workmates, championing Agile practices, and
          improving communication and productivity across the company.
  \end{itemize}

  \datedsubsection{Computer Vision Research Engineer Intern - Imperial College}{2017}
  \begin{itemize}
    \item Wrote real-time person tracker, which runs on an Android phone.
  \end{itemize}

  \datedsubsection{Financial Services Intern - Accenture}{2016}
  \begin{itemize}
    \item Wrote a web app which took complex spreadsheets of reinsurance
          data, and visualises them in an interactive manner for stakeholders.
  \end{itemize}

  \datedsubsection{Vice President - Imperial College Mental Health Society}{2015 - 2017}
  \begin{itemize}
    \item Set up Imperial's first mental health awareness society and helped
          raise over \pounds300,000 to improve Imperial's mental health services.
  \end{itemize}

  \datedsubsection{IT Officer - Imperial College Dance Club}{2014 - 2017}
  \begin{itemize}
    \item Wrote a mobile app which could be used to verify paid members, using
          an extension I wrote for the Imperial College Society API.
  \end{itemize}

  \datedsubsection{Web Developer Intern - Twofour}{2011 \& 2012}
  \begin{itemize}
    \item Built a Facebook-esque social network; complete with profiles, a newsfeed,
          friendships, image galleries, comments, and likes.
  \end{itemize}

\end{column}\begin{column}

  \section{Values}
  \begin{itemize}
    \item \textbf{Communication is key} for anything to succeed.
    \item \textbf{A sense of humour} goes a long way.
    \item \textbf{Never stop learning}, and raise those around you.
    \item \textbf{Automate testing code}. Tests, types, smart compilers. Use them.
    \item \textbf{Functional Programming {\raise.1em\hbox{= <}}3}.
  \end{itemize}

  \section{Skills}
  \subsection{Programming Languages}
    I consider myself to be a polyglot. I'm passionate about learning
    new programming languages, and keeping up to date with new paradigms.
  \begin{itemize}
    \item \textbf{Proficient} Python, Rust, Go, JavaScript/TypeScript, Shell, Java,
          SQL, C/C++, OpenGL, HTML/CSS, Haskell, Lisp+Scheme, Elixir
    \item \textbf{Familiar} OCaml, Erlang, R, MATLAB, C\#, PHP, Ruby, BrainFuck
  \end{itemize}
  \subsection{Computing Tools and Utilities}
  \begin{itemize}
    \item All OSs, CLIs, Git, Vim, VSCode, Docker, K8s, AWS, GCP, Cloudflare
  \end{itemize}

  \section{Education}
  \datedsubsection{Imperial College London}{2013 - 2017}
  MEng in Computing and Artificial Intelligence.
  \begin{itemize}
    \item \textbf{Genetic Generation of Architectural Design (Thesis)} \\
          Orchestrated a swarm of servers, to concurrently communicate with
          one another and run distributed Genetic Algorithms.
    \item \textbf{Autonomous Drone} Wrote an ML model, in C++, to allow a drone
          to autonomously fly through a programmed route.
    \item \textbf{ColDE} A web based IDE. Supports concurrent editing of Python,
          HTML, and JS, with live runtimes. Think Google Docs, but for code.
    \item \textbf{Doodlr} Allows multiple users to paint together in real-time. Supports
          complex Photoshop-esque tools and image manipulation.
    \item \textbf{PintOS} A fully featured Operating System, in C.
    \item \textbf{WACC Compiler} Compiles a C-like language to ARM Assembly.
    \item \textbf{Raspberry Pi Emulator} Wrote an ARM assembler and VM, capable
          of emulating a Raspberry Pi, all in C.
  \end{itemize}

  \section{Personal Projects}
  I have over 150 personal projects, hosted at
  \myhref{https://github.com/JCGrant}{github.com/JCGrant}.\\
  Here are some of my favourites:
  \begin{itemize}
    \item \textbf{MC Haptics} A Bluetooth haptic feedback engine, built for Minecraft.
    \item \textbf{Multiplayer RPG} An MMO architecture with entity interpolation.
    \item \textbf{Chess RS} A chess engine written in Rust.
    \item \textbf{Twitch Paints Art} Livestreamed canvas. Users can paint via chat.
    \item \textbf{Kilo} A text editor, written in C. Includes syntax HL and searching.
    \item \textbf{Blox} A proxy allowing Minecraft plugins to be written in Go.
    \item \textbf{glambda} Lambda calculus interpreter.
    \item \textbf{emojibot} AI chatbot which replies to natural language with emojis.
    \item \textbf{Postr} A Social Media with profiles, reposts, media, \& comments.
    \item \textbf{ProcGen} Various experiements in procedural generation.
    \item \textbf{Apollo} Record live music loops with friends over the internet.
  \end{itemize}

  \section{Interests + Hobbies}
  \begin{itemize}
    \item Hackathons, Leetcode, Advent of Code, Project Euler, etc.
    \item Game development.
    \item Public speaking, Debating.
    \item Salsa dancing.
    \item Guitar, Piano, Singing.
    \item Un poco de Espa\~nol.
  \end{itemize}

\end{column}

\end{document}
